Effects of Uncertainty in Heterogeneous Models

### 2017-01-24 presentation/presentation.tex
Changing the problem slide

  \item {
  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is an infinite dimensional object.
  }

  \item {
  The capital distribution must be taken into account by the agents, therefore it becomes a state variable.  
  }

>>>>

  \item {
  The introduction of aggregate uncertainty makes the distribution of wealth changing over time.
  }

  \item {
  The capital distribution must be taken into account by the agents.  
  }
